---
title: "Visual Metrics And Navigation Timings: LCP"
author: "Corey Dow-Hygelund, Mozilla Data Science"
date: 'Last Updated: `r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_document:
    theme: cosmo
    toc: true
    toc_float: true
---

```{r library_imports, message=FALSE, warning=FALSE, echo=FALSE}
library(corrplot)
library(dplyr)
library(ggplot2)
library(tidyr)
library(funModeling)
library(cowplot)
library(ggridges)
library(Boruta)
library(viridis)
library(stringr)
library(plotly)
library(earth)
library(MLmetrics)
```

```{r load, echo=FALSE, warning=FALSE, message=FALSE}
load('data/Chrome_lcp.RData')

df <- df %>%
  mutate(mode = as.factor(mode)) %>%
  mutate(url = as.factor(url))

df_orig <- df

visual_metrics <- sort(
  c(
    'firstVisualChange',
    'visualComplete85',
    'speedIndex',
    'contentfulSpeedIndex',
    'perceptualSpeedIndex'
    )
)

nav_timings <- sort(names(df)[!names(df) %in% c('mode', 'url', visual_metrics)])

df_long <- df %>%
  gather('vis_metric', 'vis_metric_value', -all_of(nav_timings), -mode, -url) %>%
  gather('nav_timing', 'nav_timing_value', -vis_metric, -vis_metric_value, -mode, -url)

vis_metrics <- c('visualComplete85', 'perceptualSpeedIndex', 'speedIndex')
vis_metrics_filter <- visual_metrics[!visual_metrics %in% vis_metrics]

num_uri <- length(unique(df$url))
```

```{r lcp_fails, echo=FALSE, warning=FALSE, message=FALSE}
lcp_url_fails <- df_orig %>%
  filter((`largestContentfulPaint.renderTime`==0) | (`largestContentfulPaint.loadTime`==0)) %>%
  count(url) 

lcp_url_rt_fails <- lcp_url_fails <- df_orig %>%
  filter((`largestContentfulPaint.renderTime`==0) ) %>%
  count(url) 

lcp_url_lt_fails <- lcp_url_fails <- df_orig %>%
  filter((`largestContentfulPaint.loadTime`==0) ) %>%
  count(url) 

lcp_odd_fails <- lcp_url_fails %>% filter(n < 5)

url_fails <- df_orig %>% filter(url %in% lcp_odd_fails$url) %>% distinct(url)
```

```{r nav_timing_states, echo=FALSE, warning=FALSE, message=FALSE}
df_state <- df_status(df %>% select(all_of(nav_timings)), print_results=FALSE)

dropped_covars <- df_state %>%
  filter((q_zeros > 0) | (q_na > 0)) %>%
  pull(variable)
```

```{r df_model_cleaning, echo=FALSE, warning=FALSE, message=FALSE}
df <- df %>%
  filter(encodedBodySize > 0)

df_rt <- df %>%
  filter(`largestContentfulPaint.renderTime` > 0)

df_non_rt <- df %>%
  filter(`largestContentfulPaint.renderTime` == 0)

df_rt_long <- df_rt %>%
  gather('vis_metric', 'vis_metric_value', -all_of(nav_timings), -mode, -url) %>%
  gather('nav_timing', 'nav_timing_value', -vis_metric, -vis_metric_value, -mode, -url)

df_lt <- df %>%
  filter(`largestContentfulPaint.loadTime` > 0)

df_lt_long <- df_lt %>%
  gather('vis_metric', 'vis_metric_value', -all_of(nav_timings), -mode, -url) %>%
  gather('nav_timing', 'nav_timing_value', -vis_metric, -vis_metric_value, -mode, -url)

```

```{r feature_sets, echo=FALSE, warning=FALSE, message=FALSE}
gen_features <- function(df){
  df_feat <- df %>% 
    # ratio of de to encodedBodySize
    mutate(ratioDeEnCoded = decodedBodySize/encodedBodySize) %>%
    # ratio of resourceCount to encodedBodySize
    # mutate(ratioRescountEncoded = resourceCount/encodedBodySize) %>%
    # ratio of page load to encodedBodySize
    mutate(rsi_encodedBodySize = rumSpeedIndex/encodedBodySize) %>% 
    # mutate(rsi_resourceCount = rumSpeedIndex/resourceCount) %>%
    mutate(lt_encodedBodySize = loadtime/encodedBodySize) %>% 
    # mutate(lt_resourceCount = loadtime/resourceCount) %>%
    # difference of responseStart
    mutate(rsi_responseStart = rumSpeedIndex-responseStart) %>% 
    mutate(rsi_requestStart = rumSpeedIndex-requestStart) %>%
    mutate(lt_responseStart = loadtime-responseStart) %>% 
    mutate(lt_requestStart = loadtime-requestStart) %>%
    # ratio of page load to durations 
    mutate(rsi_backendTime = rumSpeedIndex/backendTime) %>% 
    mutate(rsi_frontEndTime = rumSpeedIndex/frontEndTime) %>% 
    # mutate(rsi_resourceDuration = rumSpeedIndex/resourceDuration) %>%
    mutate(rsi_serverResponseTime = rumSpeedIndex/serverResponseTime) %>%
    mutate(lt_backendTime = loadtime/backendTime) %>% 
    mutate(lt_frontEndTime = loadtime/frontEndTime) %>% 
    # mutate(lt_resourceDuration = loadtime/resourceDuration) %>%
    mutate(lt_serverResponseTime = loadtime/serverResponseTime) %>%
    # ratio of durations to encodedBodySize
    mutate(bet_encodedBodySize = backendTime/encodedBodySize) %>% 
    mutate(fet_encodedBodySize = frontEndTime/encodedBodySize) %>%
    # mutate(rd_encodedBodySize = resourceDuration/encodedBodySize) %>%
    mutate(srt_encodedBodySize = serverResponseTime/encodedBodySize) 
  
  df_feat_c <- df_feat %>%
    select(-c(responseStart, responseEnd, connectStart, domainLookupStart, domainLookupEnd, fetchStart,
           domInteractive, DOMContentLoaded, firstPaint, 
           decodedBodySize, resourceCount, resourceDuration,
           redirectionTime, domainLookupTime, serverConnectionTime))
  return(df_feat_c)  
}

df_feat_rt <- gen_features(df_rt) %>%
  select(-`largestContentfulPaint.loadTime`)

df_feat_lt  <- gen_features(df_lt) %>%
  select(-`largestContentfulPaint.renderTime`)

df_feat_non_rt <- gen_features(df_non_rt) %>%
  select(-`largestContentfulPaint.loadTime`) %>%
  select(-`largestContentfulPaint.renderTime`)

df_feat_rs <- gen_features(df) %>%
  select(-`largestContentfulPaint.loadTime`) %>%
  select(-`largestContentfulPaint.renderTime`)

```

```{r modeling_arch, echo=FALSE, warning=FALSE, message=FALSE}
cv_lm_loo <- function(df, formula, response){
  urls = unique(df$url)
  cv <- NULL
  for (i in 1:length(urls)){
    # train/test samples
    train_urls <- urls[-i]
    train <- df %>% 
      filter(url %in% train_urls) 
    test <- df %>% 
      filter(!url %in% train_urls)
    # fit model
    lm_cv <- lm(formula = formula, data = train) 
    cv <- rbind(cv, data.frame(response = test[[response]],
                             prediction = predict(lm_cv, test),
                             fold = i,
                             url = test$url,
                             mode = test$mode))
  }
  return(cv)
}

generate_formula <- function(tr_cov, label, add_interactions=FALSE){
  if (add_interactions){
    formula <- paste(label, '~', paste(tr_cov, collapse="*"))
  }
  else {
    formula <- paste(label, '~', paste(tr_cov, collapse="+"))
  }
  # return(as.formula(formula))
  return(as.formula(formula))
}

run_loo_cv <- function(df, resp, cov){
  cv <- cv_lm_loo(df, 
                formula = generate_formula(cov, resp),
                      resp) %>%
    gather('metric', 'value', -response, -url, -mode, -fold)
  return(list(cv = cv, mape = MAPE(cv$value, cv$response)))
}
```
  
```{r feature_arch, echo=FALSE, warning=FALSE, message=FALSE}
gen_features <- function(df, resp){  
  features <- list()
  df_clean <- df %>% 
                  select(-c(mode, url)) %>% # select(-c(mode, url)) %>%
                  select(-c(vis_metrics)) %>%
                  select(-c(all_of(vis_metrics_filter)))
  # mars
  mars <- earth(x = df_clean, y = df %>% pull(resp))
  ev <- evimp(mars)
  features[['mars']] <- ev
  
  # boruta
  bor <- Boruta(x = df_clean, y = df %>% pull(resp)) #, doTrace = TRUE, ntree = 500, maxRuns = 1000)

  bor.df <- attStats(bor) %>%
    tibble::rownames_to_column(., 'covariate') %>%
    arrange(desc(medianImp)) %>%
    select(covariate, meanImp, medianImp)
  features[['boruta']] <- bor.df
  return(features)
}

extract_features <- function(features, additional){
  feat_f <- list()
  for(vis_metric in names(features)){
    # mars
    mars <- rownames(features[[vis_metric]][['mars']])[1:4]
    # boruta
    bor <- (features[[vis_metric]][['boruta']] %>% pull(covariate))[1:4]
    feat_f[[vis_metric]] <- list(
      # 'lcp' = additional, 
      'rumSpeedIndex' = c('rumSpeedIndex'),
      'loadtime' = c('loadtime'),
      'MARS' = mars,
      'Boruta' = bor)
    
    if(!missing(additional)){
      feat_f[[vis_metric]]['lcp'] <- additional
    }
  }
  return(feat_f)
}

model_and_eval <- function(features, df, lcp){
  feats <- extract_features(features, lcp)
  results <- list()
  for (vis_metric in names(feats)){
    for (feat_gp in names(feats[[vis_metric]])){
      results[[vis_metric]][[feat_gp]] <- run_loo_cv(df, vis_metric, feats[[vis_metric]][[feat_gp]])
    }
  }
  return(results)
}

extract_mape <- function(results){
  vis_metrics <- names(results)
  feat_gps <- names(results[[vis_metrics[1]]])
  mapes <- data.frame(matrix(ncol=length(feat_gps),nrow=0, dimnames=list(NULL, feat_gps)))
  # mapes <- list()
  for (vis_metric in vis_metrics){
    vis_m_mape <- c()
    for (feat_gp in feat_gps){
      vis_m_mape[feat_gp] <- results[[vis_metric]][[feat_gp]][['mape']]
    }
    # mapes[[vis_metric]] <- t(setNames(data.frame(vis_m_mape), c(vis_metric)))
    mapes <- rbind(mapes, t(setNames(data.frame(vis_m_mape), c(vis_metric))))
  }
  return(mapes)
}

extract_vis_features <- function(features){
  vis_metrics <- names(features)
  feats <- data.frame(matrix(ncol=length(2),nrow=0, dimnames=list(NULL, 2)))
  feats <- list()
  for (vis_metric in vis_metrics){
    vis_m_feats <- c(MARS = paste(rownames(features[[vis_metric]][['mars']])[1:4], sep = '', collapse = ', '),
                     Boruta = paste((features[[vis_metric]][['boruta']] %>% pull(covariate))[1:4], sep = '', collapse = ', '))
    # mapes[[vis_metric]] <- t(setNames(data.frame(vis_m_mape), c(vis_metric)))
    feats <- rbind(feats, t(setNames(data.frame(vis_m_feats), c(vis_metric))))
  }
  return(feats)
}

#### Generate Features Sets ####
features_rt <- list() # list('largestContentfulPaint.renderTime', 'rumSpeedIndex', 'loadTime')
features_lt <- list() #list('largestContentfulPaint.loadTime')
features_non_rt <- list()
features_rs <- list()

for (vis_metric in vis_metrics){
  features_rt[[vis_metric]] <- gen_features(df_feat_rt, vis_metric)
  features_lt[[vis_metric]] <- gen_features(df_feat_lt, vis_metric)
  features_non_rt[[vis_metric]] <- gen_features(df_feat_non_rt, vis_metric)
  features_rs[[vis_metric]] <- gen_features(df_feat_rs, vis_metric)
}
```

```{r lcp_rt_modeling, echo=FALSE, message=FALSE, warning=FALSE}
lcp_rt_res <- model_and_eval(features_rt, df_feat_rt, 'largestContentfulPaint.renderTime')

mape_lcp <- as.data.frame(extract_mape(lcp_rt_res)) %>% pull(lcp) %>%  unlist()
mape_rum <- as.data.frame(extract_mape(lcp_rt_res)) %>% pull(rumSpeedIndex) %>%  unlist()
delta_max <- round(max((mape_rum - mape_lcp) / mape_rum), 2) 
delta_min <- round(min((mape_rum - mape_lcp) / mape_rum), 2)
```

```{r lcp_lt_modeling, echo=FALSE, message=FALSE, warning=FALSE}
lcp_lt_res <- model_and_eval(features_lt, df_feat_lt, 'largestContentfulPaint.loadTime')
```

```{r lcp_non_rt_modeling, echo=FALSE, message=FALSE, warning=FALSE}
lcp_non_rt_res <- model_and_eval(features_non_rt, df_feat_non_rt)
```

```{r lcp_rs_modeling, echo=FALSE, message=FALSE, warning=FALSE}
lcp_rs_res <- model_and_eval(features_rs, df_feat_rs)
```

```{r lcp_rsi_result, echo=FALSE, warning=FALSE, error=FALSE}
extract_cv_calc_mape <- function(results_1, results_2){
  vis_metrics <- names(results_1)
  feat_gps <- names(results_1[[vis_metrics[1]]])
  mapes <- data.frame(matrix(ncol=length(feat_gps),nrow=0, dimnames=list(NULL, feat_gps)))
  cvs <- list()
  # mapes <- list()
  for (vis_metric in vis_metrics){
    vis_m_mape <- c()
    for (feat_gp in feat_gps){
      if (feat_gp == 'lcp') next
      lcp <- results_1[[vis_metric]][['lcp']][['cv']]
      # print(results_2)
      cv <- results_2[[vis_metric]][[feat_gp]][['cv']] %>%
        filter(!url %in% unique(lcp$url)) %>%
        bind_rows(lcp)
      # vis_m_mape[feat_gp] <- results_1[[vis_metric]][[feat_gp]][['mape']] # MAPE(cv$value, cv$response)
      vis_m_mape[feat_gp] <-  MAPE(cv$value, cv$response)
      cvs[[vis_metric]][[feat_gp]] <- cv
    }
    # mapes[[vis_metric]] <- t(setNames(data.frame(vis_m_mape), c(vis_metric)))
    mapes <- rbind(mapes, t(setNames(data.frame(vis_m_mape), c(vis_metric))))
  }
  return(list(mapes = mapes, cvs = cvs))
}

extract_cv_calc_mape_cmp <- function(results_1, results_2){
  vis_metrics <- names(results_1)
  feat_gps <- names(results_1[[vis_metrics[1]]])
  mapes <- data.frame(matrix(ncol=length(feat_gps),nrow=0, dimnames=list(NULL, feat_gps)))
  cvs <- list()
  # mapes <- list()
  for (vis_metric in vis_metrics){
    vis_m_mape <- c()
    for (feat_gp in feat_gps){
      lcp <- results_1[[vis_metric]][['lcp']][['cv']]
      if (feat_gp == 'lcp') {
        vis_m_mape[feat_gp] <- results_1[[vis_metric]][['lcp']][['mape']]
        
      }
      else{
        cv <- results_2[[vis_metric]][[feat_gp]][['cv']] %>%
        filter(url %in% unique(lcp$url)) 
        # vis_m_mape[feat_gp] <- results_1[[vis_metric]][[feat_gp]][['mape']] # MAPE(cv$value, cv$response)
        vis_m_mape[feat_gp] <-  MAPE(cv$value, cv$response)
        cvs[[vis_metric]][[feat_gp]] <- cv
      }
      # print(results_2)
    }
    # mapes[[vis_metric]] <- t(setNames(data.frame(vis_m_mape), c(vis_metric)))
    mapes <- rbind(mapes, t(setNames(data.frame(vis_m_mape), c(vis_metric))))
  }
  return(list(mapes = mapes, cvs = cvs))
}
```

```{r lcp_rsi_result_tbl, echo=FALSE, warning=FALSE, error=FALSE}
mapes_full <- extract_cv_calc_mape(lcp_rt_res, lcp_rs_res)
mapes_rs <- extract_mape(lcp_rs_res)

mapes_delta <- (mapes_rs - mapes_full$mapes)/mapes_rs
```


# tl;dr

[Largest Contentful Paint](https://github.com/WICG/largest-contentful-paint)(LCP) is a new page load metric that aims to be more representative of a user experience than "traditional" page load metrics. This is similar to visual metrics; however, LCP can be measured both in the lab and "in-the-wild". This report expands upon [previous work](https://metrics.mozilla.com/protected/cdowhygelund/visual_metrics_modeling.html), determining how well LCP, in addition to linear models of current page load and navigation metrics, predict visual metrics (`r paste(vis_metrics, sep='', collapse=', ')`). Linear regression models were trained on a Chrome-specific dataset of `r num_uri` URLs each ran five times. 

`largestContentfulPaint.renderTime` yields the best predictor of all visual metrics tested, though fails to be calculated for `r nrow(lcp_url_rt_fails)` URLs. The mean absolute percentage error loss (MAPE) score of this feature is lower by `r delta_min*100`-`r delta_max*100`% with respect to `rumSpeedIndex`. Conversely, `largestContentfulPaint.loadTime` is inferior to `rumSpeedIndex`, yielding higher MAPE scores for all visual metrics. 

A composite model using `largestContentfulPaint.renderTime` for cases when it is measured, while defaulting to `rumSpeedIndex` for failed URLs, yields the lowest MAPE scores. This model has `r round(min(mapes_delta$rumSpeedIndex), 2)*100` - `r round(max(mapes_delta$rumSpeedIndex), 2)*100`% improvement in predicting the visual metrics, with respect to `rumSpeedIndex` alone. 

# Dataset{.tabset}

A single dataset was provided by Andrew Creskey that contained in-house, live-site testing of Chrome across a range of URLs, to determine the efficacy of LCP. The dataset is similarly formatted as [here](https://metrics.mozilla.com/protected/cdowhygelund/visual_metrics_modeling.html#datasets), with the inclusion of the two LCP metrics. `largestContentfulPaint.renderTime` is the most accurate method when available.

* `largestContentfulPaint.renderTime`
* `largestContentfulPaint.loadTime`

The dataset was composed of `r num_uri` URLs, each run five times. Two URLs were run four times (`r paste(df_orig %>% count(url) %>% filter(n==4) %>% mutate(url_str = as.character(url)) %>% pull , sep=' ', collapse=', ')`).


## Navigation Timings
Several of the navigation metrics are not accurately measured across URLs: `r paste(dropped_covars, sep=', ')`. 

This includes the LCP metrics. 

```{r nav_timings, echo=FALSE}
knitr::kable(df_state)
```

### LCP Metrics

* `largestContentfulPaint.renderTime` fails for `r lcp_url_rt_fails %>% nrow()` URLs. 
* `largestContentfulPaint.loadTime` fails for `r lcp_url_lt_fails %>% nrow()` URLs. 

Interestingly, only `r length(url_fails)` out of `r lcp_url_rt_fails %>% nrow()` URLs that fail on `largestContentfulPaint.renderTime` have a successful measurement. Also, URLs that fail on the secondary option `largestContentfulPaint.loadTime` _do not_ fail for `largestContentfulPaint.renderTime`.


## Visual Metrics
```{r vis_metric_state, echo=FALSE, warning=FALSE, message=FALSE}
df_vis_state <- df_status(df %>% select(all_of(visual_metrics)), print_results=FALSE)
```

`contentFulSpeedIndex` appears to not be measured in Chrome. `firstVisualChange` has unusual behavior with only `r df_vis_state %>% filter(variable == 'firstVisualChange') %>% pull(unique)` unique values. 
```{r vis_metrics, echo=FALSE, warning=FALSE, message=FALSE}
knitr::kable(df_vis_state)
```

```{r vis_metric_distr, fig.width=8, fig.height=5, echo=FALSE, warning=FALSE, message=FALSE}
df_long_vis <- df %>%
  select(mode, url, vis_metrics) %>%
  gather('vis_metric', 'value', -mode, -url)

# ps = list()
#ps[['ridge']] <- 
ggplot(df_long_vis, aes(x=value, y=vis_metric, fill = factor(stat(quantile)))) +
  stat_density_ridges(
    geom = "density_ridges_gradient", calc_ecdf = TRUE,
    quantiles = 5, quantile_lines = TRUE
  ) +
  scale_fill_viridis_d(name = "Quintiles") +
  theme(axis.text.y = element_text(angle = 25, hjust = 1)) +
  xlim(0, 10000) + 
  theme_bw() +
  ylab('Visual Metric') +
  xlab('Time (ms)')
```

# Visualize
The following interactive plots display the visual metrics versus the specific page load metrics. Color represents url.
The empty values were filtered for each LCP metric. 

`largestContentfulPaint.renderTime` appears to trend better for each visual metric than `loadtime` or `rumSpeedIndex`. Specifically, the metric has an extended, less clumped, distribution for low values than `loadtime` and `rumSpeedIndex`. `largestContentfulPaint.loadTime` is similar; though is has significantly more outliers than its counterpart. 

```{r visualize, fig.width=10, fig.height=5, echo=FALSE, message = FALSE, warning=FALSE}
ggplotly(
  ggplot(df_long %>% 
           filter(nav_timing %in% c('rumSpeedIndex', 'loadtime', 'largestContentfulPaint.loadTime', 'largestContentfulPaint.renderTime')) %>%
           filter((nav_timing == 'largestContentfulPaint.loadTime' & nav_timing_value !=0) | (nav_timing != 'largestContentfulPaint.loadTime')) %>%
           filter((nav_timing == 'largestContentfulPaint.renderTime' & nav_timing_value !=0) | (nav_timing != 'largestContentfulPaint.renderTime')) %>%
           filter(!vis_metric %in% c('contentfulSpeedIndex', 'firstVisualChange')),
         aes(nav_timing_value, vis_metric_value)) +
    facet_grid(vars(vis_metric), vars(nav_timing), scales='free') + 
    geom_point(aes(color = url, shape=mode)) +
    geom_smooth(method = "lm", se = FALSE) + 
    theme_bw() + 
    theme(legend.position = "top") +
    xlab('Navigation Timing Value') + 
    ylab('Visual Metric Value') + 
    theme(legend.position = "none")
)
```


# Modeling
A realistic assessment of these metrics was performed using leaving-one-out CV across the range of URLs as described [here](https://metrics.mozilla.com/protected/cdowhygelund/visual_metrics_modeling.html#modeling). The same feature set was used as that work, though the additional features with empty values were stripped (e.g. `rd_encodedBodySize`, `ratioRescountEncoded`). In addition the five empty `encodedBodySize` records were filtered, though the feature was kept.

Three different datasets were modeled, due to the missing LCP values. This resulted in three different sets of URLs being tested in LOO CV.


* LCP: RenderTime - `largestContentfulPaint.renderTime > 0`
* LCP: LoadTime - `largestContentfulPaint.loadTime > 0` 
* Complete: "piecewise" model
    -  `largestContentfulPaint.renderTime > 0`: `largestContentfulPaint` is feature set.
    - `largestContentfulPaint.renderTime == 0`: `rumSpeedIndex` and derivatives are feature set.

Five feature sets were modeled:

* `largestContentfulPaint.renderTime` or `largestContentfulPaint.loadTime`
    - Based upon the dataset modeled.
* `rumSpeedIndex`
* `loadtime`
* Top four features selected by [MARS](https://en.wikipedia.org/wiki/Multivariate_adaptive_regression_spline)
* Top four features selected by [Boruta](https://cran.r-project.org/web/packages/Boruta/index.html)

As previously, mean absolute percentage error loss (MAPE) was calculated to rank the models. Less prediction error leads to lower MAPE scores.

## LCP: RenderTime{.tabset}
### Features
The following table displays the MARS and Boruta features selected for each visual metric.

```{r lcp_rt_final_feats, echo=FALSE}
knitr::kable(extract_vis_features(features_rt))
```


### MAPE
The following table shows the resultant MAPE scores for LCP: RenderTime dataset. 

`largestContentfulPaint.renderTime` has the lowest MAPE for all visual metrics. 


```{r lcp_rt_mape, echo=FALSE, message=FALSE, warning=FALSE}
knitr::kable(round(extract_mape(lcp_rt_res), 2))
```

## LCP: LoadTime{.tabset}
The following table displays the MARS and Boruta features selected for each visual metric.

### Features
```{r lcp_lt_final_feats, echo=FALSE, warning=FALSE, message=FALSE}
knitr::kable(extract_vis_features(features_lt))
```

### MAPE
The following table shows the resultant MAPE scores for LCP: LoadTime dataset. 

Unlike `largestContentfulPaint.renderTime`, `largestContentfulPaint.loadTime` results in a an inferior model compared to those using `rumSpeedIndex`. Both the single `rumSpeedIndex` feature model, and the composite feature model from Boruta, both result in significantly lower MAPE scores for all visual metrics. 


```{r lcp_lt_mape, echo=FALSE, message=FALSE, warning=FALSE}
knitr::kable(round(extract_mape(lcp_lt_res), 2))
```

## Complete
This model is a composite of two, designed to handle cases where `largestContentfulPaint.renderTime` is not calculated. For URLs where `largestContentfulPaint.renderTime > 0`, a linear model for `largestContentfulPaint.renderTime` is fit. 

The second model, composed of the remaining covariates, is fit on all URLs, including those where `largestContentfulPaint.renderTime > 0`. However, it is only used to predict cases where `largestContentfulPaint.renderTime == 0`. 

### Features
The table shows the features (excluding LCP) selected using all URLs. 

```{r lcp_rs_final_feats, echo=FALSE}
knitr::kable(extract_vis_features(features_rs))
```

### MAPE{.tabset}

#### LCP + rumSpeedIndex
MAPE scores for composite model:

```{r lcp_full_mape, echo=FALSE, message=FALSE, warning=FALSE}
knitr::kable(round(mapes_full$mapes, 2))
```

#### rumSpeedIndex
MAPE scores for non-LCP based models:
```{r lcp_rs_mape, echo=FALSE, message=FALSE, warning=FALSE}
knitr::kable(round(mapes_rs, 2))
```

#### Improvement
Fractional improvement in using `largestContentfulPaint.renderTime`:

```{r lcp_improve_mape, echo=FALSE, message=FALSE, warning=FALSE}
knitr::kable(round(mapes_delta, 2))
```
